The population of long-period exoplanets I. --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive

### 2016-03-03 document/ms.tex

% \renewcommand{\eqref}[1]{\ref{eq:#1}}
% \newcommand{\Eq}[1]{Equation~(\eqref{#1})}
% \newcommand{\eq}[1]{\Eq{#1}}
% \newcommand{\eqalt}[1]{Equation~\eqref{#1}}
\newcommand{\eqlabel}[1]{\label{eq:#1}}

@@

@@

\begin{eqnarray}
Q_{\mathrm{geom},k} (\params) &=& \frac{R_{\star,k}}{a_k(\params)}
    \, \frac{1 + e(\params)\,\sin\omega(\params)}{1-e(\params)^2} \\
&=& \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,R_{\star,k}
    \, \left[\frac{1 + e(\params)\,\sin \omega(\params)}{1-e(\params)^2}\right]
    \, P^{-2/3}
\end{eqnarray}

>>>>

\renewcommand{\eqref}[1]{\ref{eq:#1}}
\newcommand{\Eq}[1]{Equation~(\eqref{#1})}
\newcommand{\eq}[1]{\Eq{#1}}
\newcommand{\eqalt}[1]{Equation~\eqref{#1}}
\newcommand{\eqlabel}[1]{\label{eq:#1}}

@@

The fraction of recovered simulations as a function of the relevant parameters
gives an estimate of the search completeness or the probability of detecting
an exoplanet transit with a given set of parameters, \emph{conditioned on the
fact that it transits}.
We will call this function $Q_{\mathrm{det},k}(\params)$ where \params\ is the
set of all parameters affecting the transit detectability and $k$ is an index
running over target stars.

This detection efficiency must then be combined with the geometric transit
probability function and the window function.
For the star $k$, the geometric transit probability is given by \dfmtodo{cite}
\begin{eqnarray}
Q_{\mathrm{geom},k} (\params) &=& \frac{R_{\star,k}}{a_k}
    \, \frac{1 + e\,\sin\omega}{1-e^2} \\
&=& \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,R_{\star,k}
    \, \left[\frac{1 + e\,\sin \omega}{1-e^2}\right]
    \, P^{-2/3}
\end{eqnarray}
where the parameters $e$, $\omega$, and $P$ are included in \params.
Approximating the window function using the binomial probability of observing
at least one transit \dfmtodo{cite bm14} we find
\begin{eqnarray}
Q_{\mathrm{win},k} (\params) &=& 1 - (1 - f_{\mathrm{duty},k})^{T_k/P}
\end{eqnarray}
where $f_{\mathrm{duty},k}$ is the duty cycle and $T_k$ is the full
observation baseline for target $k$.

Combining these detection effects, the total detection efficiency is given by
\begin{eqnarray}
Q_k(\params) &=& Q_{\mathrm{det},k}(\params) \,
                 Q_{\mathrm{win},k} (\params) \,
                 Q_{\mathrm{geom},k} (\params) \quad.
\end{eqnarray}
For the purposes of this \paper, we are not considering the occurrence rate of
exoplanets as a function of stellar properties; we will only measure an
average rate across the target sample that we previously selected.
Therefore, it is sufficient to estimate the marginalized detection efficiency
integrated with respect to our prior distributions on the nuisance parameters.
In this case, the only parameters that we will consider are planet radius and
orbital period.
Under this model, the relevant detection efficiency function for long-period
transiting planets is
\begin{eqnarray}\eqlabel{full-comp}
Q(R,\,P) &=& \frac{1}{K} \sum_{k=1}^{K} \int Q_k(\params) \,
    p(\params_{\{R,\,P\}}) \dd\params_{\{R,\,P\}}
\end{eqnarray}
where $\params_{\{R,\,P\}}$ indicates the set of all parameters except radius
and period.

Since the simulated parameters in the injection and recovery tests described
above were sampled from the prior distribution $p(\params_{\{R,\,P\}})$, the
easiest way to estimate \eq{full-comp} is to take the ratio of the weighted
histogram of the recovered injections to the weighted histogram of all
simulations where each simulation is weighted by
$Q_{\mathrm{win},k} (\params) \, Q_{\mathrm{geom},k} (\params)$ evaluated at
the parameters of the simulation.

@@
